\section{Public package and reproducibility}
\label{sec:package}

The repository is organized as a paper-as-public-package: the manuscript,
certificate manifests, row-level records, replay scripts, hash manifest, and
claim-boundary ledgers are shipped together.  This follows established
reproducible-artifact practice rather than asserting a new standard; its role
here is to make the computational dependencies auditable while separating the
mathematical theorem from supplementary digital-fabrication artifacts
\cite{smith2017joss,rougier2017rescience}.  The main paper source and PDF live
in \path{paper/}.  Mathematical and certificate controls live in
\path{docs/}, \path{certified/}, \path{scripts/}, and \path{results/}.  The
public package manifest is \path{paper/PUBLIC_PACKAGE_MANIFEST.json}.

\begin{certprop}[Public package gate]
The local public package gate passes.  The command
\begin{center}
\path{python scripts/run_all_reproducibility_checks.py}
\end{center}
checks required files, B04/A7c bridge row counts, RW12 hash consistency,
manifest hashes, and absence of promoted physical-validation phrases.  The
current public package check records all checks passing.
\end{certprop}

\begin{proof}[Certification]
The generated report is \path{results/public_package_check.json}.  The pytest
wrapper \path{tests/test_public_package.py} runs the same package checker.  The
manifest records \texttt{LOCAL\_RELEASE\_GATES\_PASSED},
\texttt{public\_export\_ready=true}, and
\texttt{physical\_validation\_claimed=false}.
\end{proof}

The source-lock boundary is intentionally duplicated: the paper cites concise
Certified Propositions, while the repository ships the longer source documents
under \path{certified/source_docs/}.  In particular, the public package includes
S4 Lemmas 00--12 and the B04 contact-orientation review notes, so the bridge
source dependencies are present in the package rather than only in the private
workspace.

\begin{remark}[What the tests do not prove]
The public tests verify package integrity and row-level consistency.  They do
not replace the mathematical content of Lemmas~\ref{lem:tiling}--\ref{lem:wedge}
and Theorem~\ref{thm:wrapper}; they keep the shipped artifacts synchronized with
the claim boundary.
\end{remark}
