% Theta-star finite atlas companion addendum.
% File: theta_star_finite_atlas.tex
% This file is the promoted companion addendum entry point for the theta-star extension.
% It is intentionally separate from the main public paper theorem.

\documentclass[11pt,a4paper]{article}

\ifdefined\pdfinfoomitdate\pdfinfoomitdate=1\fi
\ifdefined\pdfsuppressptexinfo\pdfsuppressptexinfo=-1\fi
\ifdefined\pdftrailerid\pdftrailerid{}\fi

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!55!black,
  citecolor=blue!55!black,
  urlcolor=blue!55!black,
  pdftitle={Theta-Star Finite Atlas for the S4 Zero-Thickness Hinge-Tree Scaffold},
  pdfauthor={Oleksiy Babanskyy},
  pdfsubject={Local theta-star finite-atlas theorem},
  pdfkeywords={tetrahedron, hinged mechanism, theta-star, finite atlas, computational certificate}
}
\emergencystretch=2em

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\Rows}{\operatorname{Rows}}
\newcommand{\Rot}{\operatorname{Rot}}
\newcommand{\sgn}{\operatorname{sgn}}

\title{Theta-Star Finite Atlas for the S4 Zero-Thickness Hinge-Tree Scaffold:\\
A Companion Addendum}
\author{Oleksiy Babanskyy}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This companion addendum turns the theta-star proof spine for the S4 zero-thickness
hinge-tree scaffold into mathematical prose.  The scope is finite and narrow:
108 connected three-hinge trees, eight equal-magnitude sign rows per tree, and
half-angle parameter \(t=\tan(\theta/2)\) on \([0,\sqrt{3}]\).  The local theorem
classifies the theta-star values as 40 endpoint records at \(\sqrt{3}\)
(36 endpoint-free witness records plus 4 source-locked wrapper records), 8
positive-jam records at \(\sqrt{2}\), and 60 instant-jam records at \(0\).  This is a companion addendum, not a main-paper theorem update.  It does not address physical
hingeability, positive-thickness models, non-equal-angle motion, or
three-parameter classification.
\end{abstract}

\noindent\textbf{Status.} Public companion addendum for the theta-star extension.  It is promoted after external mathematical red-team. It is intentionally separate from the main paper theorem and does not broaden that theorem.

\section*{Context and related work}
This addendum sits in the computational-geometry tradition of hinged dissections, polyhedral linkages, and reproducible computational certificates.  Hinged dissections and reversible nets provide the broad geometric setting~\cite{abbott2007hinged,akiyama2018polyhedral,akiyama2016reversible,demaine2007gfalop}; continuous flattening and linkage motion give nearby motion-theoretic context~\cite{demaine2024continuous,demaine2001vertex}.  The contribution here is narrower: a finite zero-thickness equal-magnitude theta-star atlas for one source-locked S4 scaffold, tied to a public proof-spine package rather than a general hingeability theorem.


\input{sections/02_formal_objects_and_tree_status_table}
\input{sections/03_finite_angle_conjugacy}
\input{sections/04_transport_and_theta_star_invariance}
\input{sections/05_endpoint_free_class}
\input{sections/06_wrapper_scope_class}
\input{sections/07_positive_jam_class}
\input{sections/08_instant_jam_class}

\bibliographystyle{plain}
\bibliography{refs}

\end{document}
