% Local proof-prose fragment for the theta-star finite-atlas extension.
% Endpoint-free class proof. Not a standalone paper and not a main-paper update.

\section{Endpoint-free transported witness class}

The endpoint-free class has final label
\[
  \texttt{exact\_endpoint\_free\_witness\_transport\_certificate}
\]
and contains 36 target trees.  Its event value is \(\sqrt{3}\) endpoint reached.  This is an endpoint-reaching statement on the equal-magnitude ray, not a first-contact statement.

\begin{lemma}[Endpoint-free source rows]
The five representatives
\[
  \texttt{TREE\_001},\ \texttt{TREE\_004},\ \texttt{TREE\_005},\ \texttt{TREE\_027},\ \texttt{TREE\_029}
\]
have source endpoint-free witness rows over the interval \(0<t\le\sqrt{3}\).
\end{lemma}

\begin{proof}
This is the source layer recorded in the representative source certificate table.  The required predicates are the endpoint-free interval predicate, the transported separating or contact-side rows, and the explicit wording lock that \(\sqrt{3}\) is not a first-contact value.  The proof spine materializes these rows through the endpoint-free witness transport gate.
\end{proof}

\begin{lemma}[Endpoint-free transport]
Every target transported from these five representatives preserves the endpoint-free witness status over \(0<t\le\sqrt{3}\).
\end{lemma}

\begin{proof}
Apply finite-angle scaffold conjugacy and row event preservation to each transported source row.  The T5c endpoint-free witness transport gate records 36 targets and 216 transported pair rows, so each target has all pairwise witness data needed for the endpoint interval.  Root re-gauge replay ensures that non-root-preserving transports only change the common frame and do not change pairwise relative geometry.
\end{proof}

\begin{proposition}[Endpoint-free class count]
Exactly 36 trees lie in the endpoint-free transported witness class.
\end{proposition}

\begin{proof}
The T6 assembly consumes the T4 transport ledger and the T5c witness transport gate.  It checks target coverage and the final class count
\[
  \#\texttt{exact\_endpoint\_free\_witness\_transport\_certificate}=36.
\]
Together with the endpoint-free transport lemma, this gives the class contribution of 36 endpoint-reaching records at \(\sqrt{3}\).
\end{proof}
