% Local proof-prose fragment for the theta-star finite-atlas extension.
% Wrapper-scope class proof. Not a standalone paper and not a main-paper update.

\section{Source-locked wrapper class}

The wrapper class has final label
\[
  \texttt{one\_parameter\_wrapper\_scope\_source\_locked}
\]
and contains 4 target trees:
\[
  \texttt{TREE\_007},\quad \texttt{TREE\_009},\quad
  \texttt{TREE\_021},\quad \texttt{TREE\_093}.
\]
Its event value is \(\sqrt{3}\) endpoint reached, but it is deliberately kept in a separate class because its source proof is wrapper-scoped one-parameter evidence rather than the theta-star local endpoint-free source rows.

\begin{lemma}[Wrapper source lock]
The records \texttt{TREE\_007} and \texttt{TREE\_021} are source-locked to the public CL5/A7d one-parameter wrapper evidence.  The records \texttt{TREE\_009} and \texttt{TREE\_093} are source-locked to the local generalized-wedge wrapper route for the same one-parameter semantics.  None of the four records is promoted here to a physical, positive-thickness, non-equal-angle, or three-parameter statement.
\end{lemma}

\begin{proof}
The class predicate audit records that this class uses public/local wrapper artifacts and selected-hinge B04/A7c contact-side semantics.  The theta-star ledger does not reprove those wrappers.  It checks that the source references, selected hinge-side records, pair maps, and wrapper contact-side semantics needed for transport are visible.  The four tree identifiers above are therefore endpoint-reaching records only within the source-locked one-parameter wrapper scope.
\end{proof}

\begin{lemma}[Wrapper transport boundary]
Finite-angle transport can carry the wrapper-scoped endpoint-reaching status only inside the same one-parameter semantics.
\end{lemma}

\begin{proof}
The finite-angle scaffold conjugacy transports piece maps, hinge maps, sign rows, pair maps, and root re-gauges.  The source-map visibility audit exposes the selected hinge-side records required by the wrapper/contact-side semantics.  Therefore the transported records inherit the wrapper-scoped endpoint-reaching status, but no broader motion claim is introduced.
\end{proof}

\begin{proposition}[Wrapper class count]
Exactly 4 trees lie in the source-locked wrapper class.
\end{proposition}

\begin{proof}
The T6 assembly gate records and checks
\[
  \#\texttt{one\_parameter\_wrapper\_scope\_source\_locked}=4.
\]
The class remains semantically separate from the 36 endpoint-free witness records.  Both contribute endpoint-reaching records at \(\sqrt{3}\), but they have different source proof routes.
\end{proof}
