% Local proof-prose fragment for the theta-star finite-atlas extension.
% Positive-jam class proof. Not a standalone paper and not a main-paper update.

\section{Positive-jam class at sqrt(2)}

The positive-jam class has final label
\[
  \texttt{exact\_positive\_theta\_jam\_package\_source\_locked}
\]
and contains 8 target trees.  Its exact event value is
\[
  t^* = \sqrt{2}, \qquad \theta = 2\arctan(\sqrt{2}) = \arccos(-1/3), the tetrahedral bond angle.
\]

\begin{lemma}[Positive-jam source representatives]
The representatives \texttt{TREE\_000} and \texttt{TREE\_003} have exact positive-jam source packages at \(t=\sqrt{2}\).
\end{lemma}

\begin{proof}
The source table records Stage3a full-SAT contact, Stage3b no-earlier-overlap for the selected binding pair, and Stage3c non-hinge residual replay for these two representatives.  The source-map visibility audit exposes binding pair maps, support features, SAT-axis sources, and support witnesses.  The positive-jam max-over-8 certificate proves that no equal-magnitude sign row exceeds \(\sqrt{2}\), while the selected Stage3 rows attain \(\sqrt{2}\).  Therefore the representative value is exactly \(t^*=\sqrt{2}\).
\end{proof}

\begin{lemma}[Positive-jam transport]
Every target transported from \texttt{TREE\_000} or \texttt{TREE\_003} preserves the same algebraic event value \(\sqrt{2}\) and the transported binding-contact data.
\end{lemma}

\begin{proof}
By finite-angle scaffold conjugacy, the binding pair, support features, SAT-axis families, contact predicates, and no-earlier-obstruction predicates are rigidly transported with the recorded relabellings and axis-sign normalizations.  Root re-gauge does not alter pairwise relative transforms.  Thus the transported selected row attains the same blocking value.  The eight-row bijection carries the max-over-8 upper cap as well, so the target tree has \(t^*=\sqrt{2}\) without claiming exact first-contact values for every non-selected row.
\end{proof}

\begin{proposition}[Positive-jam class count]
Exactly 8 trees lie in the positive-jam class.
\end{proposition}

\begin{proof}
The T6 assembly gate records and checks
\[
  \#\texttt{exact\_positive\_theta\_jam\_package\_source\_locked}=8,
\]
and the positive-jam certificate records the closed form \(\sqrt{2}\).  This gives the class contribution of 8 trees with positive jam at the tetrahedral bond angle.
\end{proof}
