% S4 certified tetrahedral hinged mechanism --- paper source
%
% Public-facing claims are controlled by paper/CLAIM_BOUNDARY.md and
% docs/PUBLIC_CLAIM_BOUNDARY.md.  RW12 is supplementary digital material only.

\documentclass[11pt,a4paper]{article}


% Reproducible pdfLaTeX output: avoid timestamp/trailer nondeterminism so the
% built PDF can be hashed in the public package manifest.
\ifdefined\pdfinfoomitdate\pdfinfoomitdate=1\fi
\ifdefined\pdfsuppressptexinfo\pdfsuppressptexinfo=-1\fi
\ifdefined\pdftrailerid\pdftrailerid{}\fi

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs}
\usepackage{array}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!55!black,
  citecolor=blue!55!black,
  urlcolor=blue!55!black,
  pdftitle={A Scoped Zero-Thickness S4 Tetrahedral Hinge-Tree Certificate},
  pdfauthor={Oleksiy Babanskyy},
  pdfsubject={S4 tetrahedral hinged mechanism certificate package},
  pdfkeywords={tetrahedron, hinged mechanism, computational certificate, route wrapper, digital fabrication}
}
\emergencystretch=2em

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{certprop}[theorem]{Certified Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathcal T}
\newcommand{\conv}{\operatorname{conv}}
\newcommand{\Vol}{\operatorname{Vol}}
\newcommand{\Rot}{\operatorname{Rot}}
\newcommand{\sgn}{\operatorname{sgn}}
\newcommand{\Pairs}{\mathcal P}
\newcommand{\treeA}{\texttt{TREE\_007}}
\newcommand{\treeB}{\texttt{TREE\_021}}

\title{A Scoped Zero-Thickness S4 Tetrahedral Hinge-Tree Certificate:\\
Median-Plane Geometry, One-Parameter Route Wrappers, and a Selected-Hinge Contact Bridge}
\author{Oleksiy Babanskyy}
\date{}

\begin{document}
\maketitle

\begin{abstract}
We give a scoped, reproducible certificate package for a specific four-piece
(``S4'') dissection of the regular tetrahedron by two opposite-edge median
planes.  The static dissection consists of four congruent tetrahedra whose
closed union is the ambient tetrahedron.  The moving model is a zero-thickness
rigid-piece hinge-tree model on two audited representative signed rays,
\treeA{} and \treeB{}, with parameter domain
\[
  \theta=0 \quad\text{and}\quad 0<\theta\le 120^\circ.
\]
At \(\theta=0\), the pieces form a closed-contact tiling with no strict
interior overlap.  On the open ray, every unordered piece-pair obligation in
the two representative trees is routed to one of three certified predicate
layers: six selected-hinge B04 rows, four common-edge B05 rows, and two
shared-face B06/B07 rows; route-clean B03 obligations are vacuous on this
one-parameter spine.

The main theorem is intentionally narrow.  It is not a proof of physical
hingeability, positive-thickness printability, global collision-free motion, or
three-parameter bounded-cell closure.  The nontrivial semantic point is the
selected-hinge layer: an A7c signed-orientation certificate is not used alone.
A package-local B04/A7c bridge records six row-level wedge certificates showing
that the selected opening side implies boundary hinge contact and no strict
local interior overlap at the contact plane, excluding the hinge axis.  The
repository also includes RW12, a corrected body-preserving digital fabrication
handoff for \treeA{}; RW12 is supplementary digital material and not physical
validation.
\end{abstract}

\noindent\textbf{Keywords.} regular tetrahedron; hinged mechanisms; rigid-piece
kinematics; computational certificates; Sturm certificates; route wrappers;
digital fabrication handoff.

\medskip
\noindent\textbf{Companion extension note.} On the review branch
\texttt{theta-star-addendum-review}, this repository also contains a standalone
addendum-review draft for the equal-magnitude zero-thickness S4 theta-star
finite atlas under \texttt{extensions/theta\_star\_finite\_atlas/}.  That draft
has its own TeX/PDF, bibliography, proof-spine package, and review gates.  It is
not used in the theorem proved below and does not broaden the public claim
boundary of this paper.

\input{sections/01_introduction}
\input{sections/02_model_and_notation}
\input{sections/03_endpoint_and_kinematics}
\input{sections/04_one_parameter_theorem}
\input{sections/05_certificate_layers}
\input{sections/06_b04_bridge}
\input{sections/07_public_package}
\input{sections/08_rw12_boundary}
\input{sections/09_related_work}

\bibliographystyle{plain}
\bibliography{refs}

\end{document}
